A Novel Approach to Supervised Classification Using Non-Linear Metrics

### 2017-01-06 icml2017/paper.tex

% Use the following line _only_ if you're still using LaTeX 2.09.
%\documentstyle[icml2016,epsf,natbib]{article}
% If you rely on Latex2e packages, like most moden people use this:
\documentclass{article}

@@

@@

\section{Introduction}  
Supervised Classification is one of the most commonly used Machine Learning paradigms both in the industry and academic research. There is a large body of past and continuing research on the topic

@@

\section{Motivation \& Illustration Examples}

\section{Mathematical Formulation}

\section{Algorithm / Work Flow}

\section{Numerical Experiments/Results}

@@

@@

DNN - > autoencoders

\section{Conclusion}

@@

>>>>

% Use the following line _only_ if you're still using LaTeX 2.09.
%\documentstyle[icml2016,epsf,natbib]{article}
% If you rely on Latex2e packages, like most moden people use this:
\documentclass{article}
\usepackage{amsmath}

\newcommand{\mc}{\mathcal}

\def\st{{\rm s.t.}}

@@

\renewcommand{\v}[1]{{{#1}}} %\mathbf  2  \ensuremath

\newcommand{\vell}{\boldsymbol{\ell}}
\newcommand{\valpha}{\boldsymbol{\alpha}}
\newcommand{\vbeta}{\boldsymbol{\beta}}
\newcommand{\vgamma}{\boldsymbol{\gamma}}
\newcommand{\vGamma}{\boldsymbol{\Gamma}}
\newcommand{\vdelta}{\boldsymbol{\delta}}
\newcommand{\vlambda}{\boldsymbol{\lambda}}
\newcommand{\vLambda}{\boldsymbol{\Lambda}}
\newcommand{\vxi}{\boldsymbol{\xi}}
\newcommand{\vpi}{\boldsymbol{\pi}}

\newcommand{\xor}{\underline{\vee}}
\newcommand{\Xor}{\underline{\bigvee}}

@@

\paragraph{Introduction}  
Supervised Classification is one of the most commonly used Machine Learning paradigms both in the industry and academic research. There is a large body of past and continuing research on the topic

@@

\begin{itemize}
\item derive LP formulation and procedure to improve metric
\item propose algorithm to report outliers and suggest regions which needs more samples

\item iterative algorithm for training NN ?????

\item TODO
\end{itemize}

 \clearpage 
\section{Motivation \& Illustration Examples}

\subparagraph{Distance Learning}

\subparagraph{Outlier Detection \& Further Sampling Recommendation}

\subparagraph{Interactive Sampling Procedure}

\clearpage
\section{Mathematical Formulation}

\begin{equation}
\mc{F} = \{ (\v{a},\v{B},\v{d}) \in \Re^p \times \Re^{p \times p} \times \Re_+^{N \times N} : \v{B}~\text{symmetric}, d_{ij} = \v{a}^{\top}
\vdelta_{ij} + \vdelta_{ij}^{\top} \v{B}\vdelta_{ij} \quad \forall i,j \in \mc{N} \}
\end{equation}
or
\begin{subequations} \label{set:feasible_region_distance_metric}
\begin{alignat}{4}
%\mc{F} = \Bigg\{ \v{a},\v{B},\v{d} : &  &&  \\
    & d_{ij} = \sum_{k=1}^p \delta_{ijk} a_{k} + %\sum_{k=1}^p \delta_{ijk}^2 b_{kk} + 2 \sum_{k=1}^{p-1} \sum_{\ell=k+1}^p  \delta_{ijk} \delta_{ij\ell} b_{k\ell} && \qquad \forall i,j \in \mc{N} \label{eq:distance_metric_def} \\
%    & 0 \leq d_{ij} \leq 1 && \qquad \forall i,j \in \mc{N} \\
 %   & \v{a} \in \Re^p && \\ 
    & b_{k\ell} \in \Re && \qquad \forall k=1,\dots,p, \ell=k,\dots,p \Bigg\}
\end{alignat}
\end{subequations}

\begin{subequations} \label{model:epsilon_lp_1}
\begin{alignat}{4}
\max_{{a},{B},{d},\epsilon}~~& \epsilon &&  \\
\st~~& \epsilon \leq d_{ik} && \qquad \forall i \in \mc{N}, k \in \mc{N}\backslash\mc{C}_i \label{eq:epsilon_lp_separation_constr_t} \\
    & \eqref{set:feasible_region_distance_metric} & & 
\end{alignat}
\end{subequations}
Let $\epsilon^{\max}$ be the maximum non-neighbor separation, i.e., the optimal value of $\epsilon$ in \eqref{model:epsilon_lp_1}.

Given $\epsilon \in (0,\epsilon^{\max}]$, model \eqref{model:1} can be expressed as a linear programming feasibility problem:
\begin{subequations} \label{model:big_lp_1}
\begin{alignat}{4}
\max_{\v{a},\v{B},\v{d},\v{t}}~~& \sum_{i \in \mc{N}} t_i &&  \\
\st~~& t_i + \epsilon \leq d_{ik} && \qquad \forall i \in \mc{N}, k \in \mc{N}\backslash\mc{C}_i \label{eq:big_lp_separation_constr_t} \\
    & t_i \leq d_{ij} && \qquad \forall i \in \mc{N}, j \in \mc{C}_i \label{eq:big_lp_dual_constr_t} \\
    & t_i \geq 0 & & \qquad \forall i \in \mc{N} \\
    & \eqref{set:feasible_region_distance_metric} & & 
\end{alignat}
\end{subequations}
For $\epsilon \in (0,\epsilon^{\max}]$, model \eqref{model:big_lp_1} is always feasible since the origin $\v{0}$ is always feasible.
Note that $t_i$ represents the distance to point $i$'s nearest neighbor since constraints \eqref{eq:big_lp_dual_constr_t} ensure that $t_i \leq \min_{j \in \mc{C}_i} d_{ij}$,
while the objective function encourages $t_i = \min_{j \in \mc{C}_i} d_{ij}$ for all $i$.
Meanwhile, constraints \eqref{eq:big_lp_separation_constr_t} ensure that the separation $[\min_{k \in \mc{N}\backslash\mc{C}_i} d_{ik}] - [\min_{j \in \mc{C}_i} d_{ij}]$ is at least $\epsilon$.
If model \eqref{model:big_lp_1} returns a feasible solution with $t_i^* = \min_{j \in \mc{C}_i} d_{ij}^* > 0$ for all $i \in \mc{N}$, then the distance metric satisfies requirements 1-3.
Otherwise there exists a subset $\mc{O}$ of outlier points such that $0 \leq t_i^* < \min_{j \in \mc{C}_i} d_{ij}^*$ for all $i \in \mc{O}$, which means that no such distance metric guaranteeing a minimum separation exists for the choice of $\epsilon$.

\clearpage 
\section{Algorithm / Work Flow}

\clearpage
\section{Numerical Experiments/Results}

\subsection{Outlier Detection and Further sampling recommendation}

In the experiment we took MNIST and CIFAR100 dataset

we used  auto-encoders and then run Algorithm XXX

Cifra 
[7, 35, 64, 71, 73, 81]

\includegraphics[scale=.1]{fig/c5.eps}
\includegraphics[scale=.1]{fig/c6.eps}
\includegraphics[scale=.1]{fig/c12.eps}

outlier
\includegraphics[scale=.1]{fig/c7.eps}

\includegraphics[scale=.1]{fig/c8.eps}
\includegraphics[scale=.1]{fig/c10.eps}

MNIST
[120]

\includegraphics[scale=.1]{fig/MNIST119.eps}
\includegraphics[scale=.1]{fig/MNIST121.eps}
\includegraphics[scale=.1]{fig/MNIST122.eps}
\includegraphics[scale=.1]{fig/MNIST124.eps}

ourlier
\includegraphics[scale=.1]{fig/MNIST120.eps}

In Figure \ref{fig:AE}
\begin{figure}

\todo[inline,color=green]{TODO}
\caption{TODO}
\label{fig:AE}

\end{figure}

@@

we run NN
on following datasets, using 
$\ell_1, \ell_2, \ell_\infty$ distance measure
and compare it with the optimal distance measure we have train by our procedure

In Figure \ref{fig:NN-exp}
\begin{figure}

\todo[inline,color=green]{TODO}
\caption{TODO}
\label{fig:NN-exp}

\end{figure}

\begin{table}
\caption{Comparison of testing error of NN with different metrics.}
\label{tbl:BD-NN}
\begin{tabular}{l|r|r|r|r}
dataset & NN-$\ell_1$ 
		& NN-$\ell_2$
		& NN-$\ell_\infty$
        & NN-B
\\        
a1a
\\
a9a
\\
covtype
\\
mushrooms
\\
splice
\\
iris
\\
breast-cancer
\end{tabular}

\end{table}

@@

\clearpage 
\section{Conclusion}

@@

\clearpage 
\appendix

\onecolumn 
\section{Proofs}

$$ TODO $$
